\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-30 journalWallFriction/experiment.tex
Changed Figure 7 description.
cleaned results

To obtain experimental data, the test samples (the phantom intestine model and the bovine cross section) were placed in laser-cut acrylic discs and then immersed in corn syrup. Corn syrup was used to increase the viscosity to 12000 cP for the experiments. Spherical $\SI{1}{\milli\metre}$ magnets (supermagnetman \#SP0100-50) were used as our particles. Our experimental setup did not perfectly implement the system dynamics in \eqref{eq:swarmDynamicsAndFric}. In particular, the magnetic field in this setup is only approximately uniform. The magnetic force varies in both magnitude and orientation. As shown in the video attachment, this non-uniformity causes the particle closer to the coil to move faster than the other particle. Also, magnetic forces are not exactly parallel, but point toward the center of the activated coil. Algorithm~\ref{alg:optimalAlg} can still work with  these non-uniformities, but sometimes requires additional iterations.

@@

The intestine phantom model was used first and was made to mimic the geometry of an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and 60 $\SI{2}{\milli\metre}$ long protrusions on its inner surface cut out of $\SI{6}{\milli\metre}$ thick acrylic to model the geometry of intestinal villi. Fig.~\ref{fig:story} top row shows an experiment. Starting and ending positions were printed beneath the workspace on transparency film.

@@

Strips of cow stomach approximately $\SI{5}{\milli\metre}$ thick were cut and sewn to acrylic cylinder and then glued to an acrylic substrate using cyanoacrylate (superglue). This assembly was then filled with corn syrup. The experiment is shown in Fig.~\ref{fig:story} bottom row. Video of this experiment is available in the supplementary materials.
%In using the small intestines, which were about 25mm in diameter, the resulting workspace was less than half of that of our simulated intestines. This meant more care had to be taken in navigating the magnets to their goal locations to avoid getting them too close to each other.

>>>>

To obtain experimental data, the test samples (the phantom intestine model and the bovine cross section) were placed in laser-cut acrylic discs and then immersed in corn syrup. Corn syrup was used to increase the viscosity to 12000 cP for the experiments. Spherical $\SI{1}{\milli\metre}$ magnets (supermagnetman \#SP0100-50) were used as our particles. Our experimental setup did not perfectly implement the system dynamics in \eqref{eq:swarmDynamicsAndFric}. In particular, the magnetic field in this setup is only approximately uniform. The magnetic force varies in both magnitude and orientation. As shown in the video attachment, this non-uniformity causes the particle closer to the coil to move faster than the other particle. This phenomenon makes it easier to increase particle separation than to decrease separation, but this can be compensated because boundary collisions easily decrease the separation. Also, magnetic forces are not exactly parallel, but point toward the center of the activated coil. Algorithm~\ref{alg:optimalAlg} still works despite these non-uniformities, but sometimes requires additional iterations.

@@

The intestine phantom model was used first and was made to mimic the geometry of an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and 60 $\SI{2}{\milli\metre}$ long protrusions on its inner surface cut out of $\SI{6}{\milli\metre}$ thick acrylic to model the geometry of intestinal villi. Figure \ref{fig:story} top row shows an experiment. Starting and ending positions were printed beneath the workspace on transparency film. Our algorithm successfully delivered the particles to goal positions in 10 out of 10 trials.

@@

Strips of cow stomach approximately $\SI{5}{\milli\metre}$ thick were cut and sewn to acrylic cylinder and then glued to an acrylic substrate using cyanoacrylate (superglue). This assembly was then filled with corn syrup. The experiment is shown in Fig.~\ref{fig:story} bottom row. Our algorithm successfully delivered the particles to goal positions in 5 out of 5 trials.
A video showing one trial of this experiment is available in the supplementary materials. 
%In using the small intestines, which were about 25mm in diameter, the resulting workspace was less than half of that of our simulated intestines. This meant more care had to be taken in navigating the magnets to their goal locations to avoid getting them too close to each other.

### 2018-05-30 journalWallFriction/theory2robAlgs.tex
cleaned results

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} shows reachable sets for a square workspace. There are four reachable sets, the horizontal (and vertical) reachable sets are equivalent in the  $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle hits edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{figure}
\centering
\begin{overpic}[width=0.95\columnwidth]{zaxis.pdf}\end{overpic}
\caption{\label{fig:zaxis}
Illustration on how boundary contacts enable 3D positioning. Once one particle contacts a boundary, the other particle's 2-move reachable set is a prism formed by extending the 2D 2-move reachable set in the $\pm z$-direction.
} %\vspace{-1em}
\end{figure}

>>>>

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} highlights the construction of the 2-move reachable sets for a square workspace. There are four 2-move reachable sets, but the horizontal (and vertical) reachable sets are equivalent in the $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle hits edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{figure}
\centering
\begin{overpic}[width=0.95\columnwidth]{zaxis.pdf}\end{overpic}
\caption{\label{fig:zaxis}
Illustration on how boundary contacts enable 3D positioning. Once one particle contacts a boundary, the other particle's 2-move reachable set is a prism formed by extending the 2D 2-move reachable set in the $\pm z$ direction.
} %\vspace{-1em}
\end{figure}
